### 2022-08-25 manuscript.Rmd
Update chunk options

# Set global options
options(readr.show_col_types = FALSE)
opts_chunk$set(
  fig.pos = "tp",
  fig.width = 12,
  include = FALSE,
  message = FALSE,
  out.width = "100%",
  warning = FALSE
)

@@

```{r, eeg_processing}
# Define function for processing behavioral log files
read_log <- function(log_file) {

@@

```{r, mixed_models}
# Construct model formula
form <- ~ phase * condition +
  (phase * condition | participant_id) +
  (phase * condition | item_id)

@@

```{r, fig1, include=TRUE, fig.height=12, fig.cap="(ref:figure-1-caption)"}
# Create Figure 1
plot_fig1(files_dir, evokeds, config, channel_locations, models)
```

@@

```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)", include=TRUE, eval=TRUE}
# Create topographic plots for event-related power in the pre-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive"),
  p_cluster = p_cluster
)
```

@@

```{r, fig3, fig.height=11, fig.cap="(ref:figure-3-caption)", include=TRUE, eval=TRUE}
# Create topographic plots for event-related power in the insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive"),
  p_cluster = p_cluster
)
```

@@

```{r, fig4, fig.height=11, fig.cap="(ref:figure-4-caption)", include=TRUE, eval=TRUE}
# Create topographic plots for event-related power in the post-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(
    tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive"
  ),
  p_cluster = p_cluster
)
```

@@

```{r, control_analysis}
# (Re-)do the actual model fitting if requested
if (run$control_analysis) {

@@

```{r tabs1, include=TRUE, results="asis"}
# Print table of materials
read_tsv(here("materials", "items.txt"), col_types = cols()) %>%
  mutate(
    match_ger = paste0(match_noun_ger, ", ", match_verb_ger),
    match_en = paste0("{[", match_noun_en, ", ", match_verb_en, "]}"),
    nonmatch_ger = paste0(nonmatch_noun_ger, ", ", nonmatch_verb_ger),
    nonmatch_en = paste0("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
  ) %>%
  transmute(
    img = paste0(
      "\\includegraphics[valign=c,scale=0.245]{materials/unfamiliar/",
      item,
      ".png}"
    ),
    item = as.character(item),
    match = paste(match_ger, match_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n"),
    nonmatch = paste(nonmatch_ger, nonmatch_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n")
  ) %>%
  apa_table(
    booktabs = TRUE,
    col.names = c(
      "Stimulus", "ID", "Matching keywords", "Non-matching keywords"
    ),
    escape = FALSE,
    longtable = TRUE,
    caption = "Unfamiliar Object Stimuli\\smallskip",
    font_size = "footnotesize"
  )
```

@@

```{r, ress1a, include=TRUE}
# Helper function for printing model summary, ANOVA (F tests), and contrasts
print_model_outputs <- function(model_object) {
  model <- model_object$model
  model@call$data <- NULL # Prevents cluttering the `summary` output
  print(summary(model))
  cat("\n")
  print(model_object$anova)
  cat("\nFollow-Up Contrasts (Simple Effects)\n")
  print(model_object$contrasts)
  cat("\n\n")
}

@@

```{r, ress1b, include=TRUE}
# Print model outputs
print_model_outputs(models$N170)
```

@@

```{r, ress1c, include=TRUE}
# Print model outputs
print_model_outputs(models$N400)
```

@@

```{r, figtfrclusters, fig.height=12, include=TRUE}
# Plot thresholded cluster images for the insight phase
tfr_clusters %>%
  filter(contrast == "Insight/Informed - Insight/Naive" & p_val < .05) %>%
  ggplot(aes(x = time, y = freq, fill = cluster)) +
  facet_wrap(~channel) +
  geom_raster() +
  theme(legend.position = "top")

>>>>

# Set global options
options(readr.show_col_types = FALSE)
opts_chunk$set(
  fig.pos = "tp",
  fig.width = 12,
  message = FALSE,
  out.width = "100%",
  warning = FALSE
)

@@

```{r, eeg_processing, include=FALSE}
# Define function for processing behavioral log files
read_log <- function(log_file) {

@@

```{r, mixed_models, include=FALSE}
# Construct model formula
form <- ~ phase * condition +
  (phase * condition | participant_id) +
  (phase * condition | item_id)

@@

```{r, fig1, fig.height=12, fig.cap="(ref:figure-1-caption)"}
# Create Figure 1
plot_fig1(files_dir, evokeds, config, channel_locations, models)
```

@@

```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)"}
# Create topographic plots for event-related power in the pre-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Pre-insight"),
  filter(tfr_clusters, contrast == "Pre-insight/Informed - Pre-insight/Naive"),
  p_cluster = p_cluster
)
```

@@

```{r, fig3, fig.height=11, fig.cap="(ref:figure-3-caption)"}
# Create topographic plots for event-related power in the insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(tfr_clusters, contrast == "Insight/Informed - Insight/Naive"),
  p_cluster = p_cluster
)
```

@@

```{r, fig4, fig.height=11, fig.cap="(ref:figure-4-caption)"}
# Create topographic plots for event-related power in the post-insight phase
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Post-insight"),
  filter(
    tfr_clusters, contrast == "Post-insight/Informed - Post-insight/Naive"
  ),
  p_cluster = p_cluster
)
```

@@

```{r, control_analysis, include=FALSE}
# (Re-)do the actual model fitting if requested
if (run$control_analysis) {

@@

```{r tabs1, results="asis"}
# Print table of materials
read_tsv(here("materials", "items.txt"), col_types = cols()) %>%
  mutate(
    match_ger = paste0(match_noun_ger, ", ", match_verb_ger),
    match_en = paste0("{[", match_noun_en, ", ", match_verb_en, "]}"),
    nonmatch_ger = paste0(nonmatch_noun_ger, ", ", nonmatch_verb_ger),
    nonmatch_en = paste0("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
  ) %>%
  transmute(
    img = paste0(
      "\\includegraphics[valign=c,scale=0.245]{materials/unfamiliar/",
      item,
      ".png}"
    ),
    item = as.character(item),
    match = paste(match_ger, match_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n"),
    nonmatch = paste(nonmatch_ger, nonmatch_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n")
  ) %>%
  apa_table(
    booktabs = TRUE,
    col.names = c(
      "Stimulus", "ID", "Matching keywords", "Non-matching keywords"
    ),
    escape = FALSE,
    longtable = TRUE,
    caption = "Unfamiliar Object Stimuli\\smallskip",
    font_size = "footnotesize"
  )
```

@@

```{r, ress1a}
# Helper function for printing model summary, ANOVA (F tests), and contrasts
print_model_outputs <- function(model_object) {
  model <- model_object$model
  model@call$data <- NULL # Prevents cluttering the `summary` output
  print(summary(model))
  cat("\n")
  print(model_object$anova)
  cat("\nFollow-Up Contrasts (Simple Effects)\n")
  print(model_object$contrasts)
  cat("\n\n")
}

@@

```{r, ress1b}
# Print model outputs
print_model_outputs(models$N170)
```

@@

```{r, ress1c}
# Print model outputs
print_model_outputs(models$N400)
```

@@

```{r, figtfrclusters, fig.height=12, include=FALSE}
# Plot thresholded cluster images for the insight phase
tfr_clusters %>%
  filter(contrast == "Insight/Informed - Insight/Naive" & p_val < .05) %>%
  ggplot(aes(x = time, y = freq, fill = cluster)) +
  facet_wrap(~channel) +
  geom_raster() +
  theme(legend.position = "top")
